---
title: "Exercise 6b: ANOVA"
author: "Your-name-here"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(car)
```

## Example 1: Comparing bill length across species of penguins

We would like to know if the mean bill length varies between species of penguins included in the `palmerpenguins` dataset. We know the dataset pretty well at this point, so let's go ahead and load it:

```{r}
penguins <- penguins

```


#### Q1.1. Start by visualizing the distribution of bill length across the groups using a boxplot. Remember to think about what your continuous variable is and what your grouping variable is.

```{r}
ggplot(data = ---, aes(x = ---, y = ---))+
  geom_boxplot()

```

#### Q1.2. From the boxplots above, do you think it's likely that the groups differ in mean bill length? And if so, which group(s) do you think are different?


#### Q1.3. Given the number of groups and the type of variable you'd like to compare across them, which type of test should you use? 



### Q1.4. Let's start off by stating our null and alternate hypothesis.

H~0~: 
H~1~:  


#### Q1.5. What are the assumptions for this test? 




#### Q1.6. Test the normality assumption

```{r}
qqPlot(---)

shapiro.test(---)
```

#### Q1.7. Test the homogeneity of variance assumption

```{r}
leveneTest(--- ~ ---,  data = ---)
```

#### Q1.8. You've now got an example where a single individual has thrown off your Shapiro test. Consider that the Gentoo species has met normality. Other than that test, have the assumptions for the ANOVA analysis been met? 



#### Q1.9. Perform the ANOVA analysis

```{r}
anova1 <- aov(--- ~ ---,  data = ---)
summary(anova1)
```

#### Q1.10. Consider the results from your ANOVA test. What do you conclude about your null hypothesis?



#### Q1.11. Perform your post-hoc test. Between which groups does there seem to be a difference?

```{r}
TukeyHSD(---)

```

## Example 2: Displacement in engines with different numbers of gears

We're interested in knowing whether engines with different gears have different displacement - that is, the volume moved by an engine. The data is contained in the `mtcars` data which is loaded with `dplyr`


```{r}
mtcars <- mtcars

mtcars <- mtcars %>% 
  mutate(gear = as.factor(gear))

```


#### Q2.1. Start by visualizing the distribution of `disp` across the groups using a boxplot. Remember to think about what your continuous variable is and what your grouping variable is.

```{r}
ggplot(data = ---, aes(x = ---, y = ---))+
  geom_boxplot()

```

#### Q2.2. From the boxplots above, do you think it's likely that the groups differ in displacement? And if so, which group(s) do you think are different?



#### Q2.3. Given the number of groups and the type of variable you'd like to compare across them, which type of test should you use? 



### Q2.4. Let's start off by stating our null and alternate hypothesis.

H~0~: 
H~1~: 


#### Q2.5. What are the assumptions for this test? 




#### Q2.6. Test the normality assumption

```{r}
qqPlot(---)

shapiro.test(---)
```


#### Q2.7. Test the homogeneity of variance assumption

```{r}
leveneTest(--- ~ ---,  data = ---)
```

#### Q2.8. You've now got an example where the p-value for normality is marginal. Consider that the 4-gear group has met normality. Other than that test, have the assumptions for the ANOVA analysis been met? 



#### Q1.9. Perform the ANOVA analysis

```{r}
anova2 <- aov(--- ~ ---,  data = ---)
summary(anova2)
```

#### Q1.10. Consider the results from your ANOVA test. What do you conclude about your null hypothesis?


#### Q1.11. Perform your post-hoc test. Between which groups does there seem to be a difference?



```{r}
TukeyHSD(---)
```