---
title: "Kruskal Wallis"
author: "Your-name-here"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(car)
library(FSA)

child <- read.csv("wellbeing-scores.csv")

```


## 1. Child wellbeing scores 

We are working in a hospital unit and have been posted in a pediatric unit. Every few hours, a nurse is asked to assess the condition of patients in the unit. Condition is  scored on an ordinal Likert scale: 5 codes for very good, 3 for neither good nor bad, and 1 for very bad. We have three patients which have been assessed 10 times each. Their scores are contained in the `child` dataset. We want to know, do their scores differ? 


#### Q1.1. Start by making a plot of the data, showing differences in the distribution of scores between the two patients. 

Note: There are multiple ways to do this! 

```{r }


```

#### Q1.3. Assess normality of scores for each patient. Should we use a parametric or non-parametric test?

```{r}


```

#### Q1.3. Which type of non-parametric test should we use?



#### Q1.4. State the null and alternate hypotheses

H~0~: 

H~1~: 


#### Q1.5. Run the test 

```{r}

```

#### Q1.6. Conclude on your null hypothesis:

```{r}


```

#### Q1.7. Which group(s) differ from the others and in what direction? You might use here the Dunn test as well as your initial plot to help you interpret the Dunn test





