---
title: "Kruskal Wallis"
author: "Your-name-here"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(car)
library(FSA)

child <- read.csv("wellbeing-scores.csv")

```


## 1. Child wellbeing scores 

We are working in a hospital unit and have been posted in a pediatric unit. Every few hours, a nurse is asked to assess the condition of patients in the unit. Condition is  scored on an ordinal Likert scale: 5 codes for very good, 3 for neither good nor bad, and 1 for very bad. We have three patients which have been assessed 10 times each. Their scores are contained in the `child` dataset. We want to know, do their scores differ? 


#### Q1.1. Start by making a plot of the data, showing differences in the distribution of scores between the two patients. 

Note: There are multiple ways to do this! 

```{r}

ggplot(child, aes(x = patient, y = score))+
  geom_violin()+
  geom_boxplot(width = 0.25)

ggplot(child, aes(x = score, fill = patient))+
  geom_histogram(position = "dodge")+
  facet_grid(patient ~ .)

ggplot(child, aes(x = score, fill = patient))+
  geom_density(alpha = 0.5)+
   facet_grid(patient ~ .)+
  scale_fill_viridis_d()

```

#### Q1.3. Assess normality of scores for each patient. Should we use a parametric or non-parametric test?

Non-parametric 

```{r}
child1 <- filter(child, patient == "Child 1")
shapiro.test(child1$score)
qqPlot(child1$score)

child2 <- filter(child, patient == "Child 2")
shapiro.test(child2$score)
qqPlot(child2$score)

child3 <- filter(child, patient == "Child 3")
shapiro.test(child3$score)
qqPlot(child3$score)


```

#### Q1.3. Which type of non-parametric test should we use?

Kruskal Wallis because we have three groups


#### Q1.4. State the null and alternate hypotheses

H~0~: The median observation scores do not differ across patients

H~1~: The median observation scores **DO** differ across patients


#### Q1.5. Run the test 

```{r}

kruskal.test(score ~ patient, data = child)

```

#### Q1.6. Conclude on your null hypothesis:

Reject the null hypothesis ( p <0.05)

#### Q1.7. Which group(s) differ from the others and in what direction? You might use here the Dunn test as well as your initial plot to help you interpret the Dunn test

Child 2 is different, child 2 has lower scores than child 1 or 3 which have similar scores 

```{r}
dunnTest(score ~ patient, data = child, method = "bh")

```





