---
title: "Joining, pivoting, summarizing across groups"
author: "Your-name-here"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 1. Summarizing by groups 

For this, we will work with the Ache dataset again. It's available as a .csv in your working directory. Load it with the `read.csv()` function and save it as `ache`

```{r}
ache <- read.csv("ache-hunting.csv")
```

If you don't remember what the data looks like, go ahead and insert a code chunk and look at the structure of the data. 

#### Q1.1.  Produce the summary statistics for `ache$age`. We're going to use these to break the ages into four roughly equal groups, so make sure to use the median and quartiles. You can compute the quartiles with `quantile()`, specifying the 0.25 and 0.75 probabilities.

```{r}

```

#### Q1.2 Use the computed Q1, median and Q3 values, combined with `mutate()` and an `ifelse()` statement to compute a new variable called "agegroup" with the levels: 1, 2, 3, 4. Go ahead and save the resulting dataframe as `ache`.

```{r}

```

#### Q1.3. Based on our previous knowledge of the returns from Ache hunts (assignment 1 is due soon!), we know that a lot of hunts are unsuccessful. But of the hunts that are successful, is there any difference between age groups in average meat return? Make sure to also produce standard deviations!
Hint: Use `group_by()` and `summarise()`

```{r}

```

#### Q1.4. Is there any difference in yield per hunt between the age groups when we exclude the hunts that are unsuccessful? Produce a plot to demonstrate the summary statistics you produced in Q1.3. Make sure to color your plot by age group and add informative labels on the title and axes.

```{r}

```

## 2. Pivoting

For this exercise, You will use the following datasets, which are messy: 

```{r}
table4b <- table4b
table4a <- table4a
```

`table4a` contains counts of cases for 1999 and 2000 across several countries. `table4b` contains population values for 1999 and 2000 across several countries 

#### Q2.1. Have a look at both datasets. 

```{r}

```

#### Q2.2. Which are the columns that should be pivoted longer?

#### Q2.3. Pivot the tables longer, and save them as `table4a` and `table4b` (overwrite the old versions)

```{r}


```


## 3. Joining 

Now, let's plan to join the two datasets that were pivoted longer: `table4a` and `table4b`. 

#### Q3.1. Let's start be identifying the columns that are shared. Visualize the structure of both dataframes, then list the columns that are repeated: 

```{r}

```

#### Q3.2. Given the columns that overlap between the datasets, what kind of join would be appropriate? If you are choosing `left_join()` or `right_join()`, specify which dataframe is on the right or left. 


#### Q3.3. Perform the join, specifying column(s) to join by, and save the resulting dataframe as a new object. Print the new dataframe to check your work.

```{r}


```

